
% --- PHASE 1 ---
\subsection{Phase 1: Foundation and Validation (Quarters 1-2)}
\textbf{Strategic Objective:} To transform the prototype into a stable and secure MVP, acquire the first early adopters, and \textbf{validate the core product and pricing model hypotheses through a targeted partnership program.}

\subsubsection{Product Development \& Engineering}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q1:}
    \begin{itemize}
        \item \textbf{Stabilization:} Complete the test suite (unit, integration) to ensure the reliability of the core engine.
        \item \textbf{Plugin:} Finalize and document the internal system to enable standardized plugin development.
        \item \textbf{UI/UX:} Refine the hybrid IDE interface to resolve any synchronization issues and improve the user experience.
        \item \textbf{On-Premise:} Develop and test the on-premise version of the platform for enterprise customers.
    \end{itemize}
    \item \textbf{Q2:}
    \begin{itemize}
        \item \textbf{Authentication:} Implement a robust user management and authentication system.
        \item \textbf{Onboarding:} Develop a guided onboarding wizard for new users.
        \item \textbf{Store (v1):} Create the API and UI for the first version of the Automation Store (read-only).
    \end{itemize}
\end{itemize}

\subsubsection{Go-to-Market (Marketing \& Sales)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q1-Q2:}
    \begin{itemize}
        \item \textbf{Vertical Strategy:} Define a detailed Ideal Customer Profile (ICP) within an \textit{initial vertical niche} (e.g., BioTech/Scientific Research, based on the user case of Esplorado).
        \item \textbf{(New) Design Partner Program:} Launch an exclusive program for 3-5 selected companies in the target vertical. Offer early access and direct support in exchange for continuous feedback and a potential preliminary contract.
    \end{itemize}
    \item \textbf{Q3-Q4:}
    \begin{itemize}
        \item \textbf{Niche Launch:} Execute the launch on Product Hunt, Hacker News, and relevant channels, with communication focused on the chosen vertical.
        \item \textbf{Feedback Collection:} Gather structured feedback from both Free Tier users and, with priority, from Design Partners.
    \end{itemize}
\end{itemize}

\subsubsection{Community \& Ecosystem Management}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q1-Q2:}
    \begin{itemize}
        \item \textbf{Targeted Plugin Development:} Develop and document the first "official" plugins, giving \textit{priority to those most relevant to the target vertical}.
    \end{itemize}
    \item \textbf{Q3-Q4:}
    \begin{itemize}
        \item \textbf{Community Creation:} Launch the official Discord/Slack server.
        \item \textbf{Engagement:} Founders and the development team will actively participate to answer questions and create a welcoming environment.
    \end{itemize}
\end{itemize}

\subsubsection{General \& Corporate Operations}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q1-Q2:}
    \begin{itemize}
        \item \textbf{Legal and Administrative Setup:} Finalize the corporate structure, open bank accounts.
        \item \textbf{(New) Partner Contracting:} Prepare the agreements for the "Design Partner Program."
    \end{itemize}
    \item \textbf{Q3-Q4:}
    \begin{itemize}
        \item \textbf{Terms of Service Definition:} Write and publish the Terms of Service and Privacy Policy for the Free Tier launch.
    \end{itemize}
\end{itemize}

\clearpage

% --- PHASE 2 ---
\subsection{Phase 2: Expansion and Growth (Quarters 3-4)}
\textbf{Strategic Objective:} To scale user acquisition, expand the ecosystem, and implement the necessary enterprise features for monetization, based on the data validated in Phase 1.

\subsubsection{Product Development \& Engineering}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q5-Q6:}
    \begin{itemize}
        \item \textbf{Security:} Implement a secrets management system for credentials.
        \item \textbf{Versioning:} Add history and rollback functionality for automations.
    \end{itemize}
    \item \textbf{Q7-Q8:}
    \begin{itemize}
        \item \textbf{Observability:} Develop the first version of the data platform for flow performance metrics.
        \item \textbf{Improve Dashboards:} Create a user interface for visualizing flows.
        \item \textbf{Proactive AI:} Implement basic "auto-healing" features based on flow performance data.
