
\textbf{Free-to-Paid Conversion Rate:} >3\%.
\textbf{MRR Growth Rate:} Consistent month-over-month growth.
\\
\addlinespace
\textbf{Ecosystem Partnerships} &

\textbf{Strategic Integrations:} Actively develop plugins for 2-3 complementary tech platforms with a similar user base.
\textbf{Co-Marketing:} Launch joint marketing campaigns with partners (webinars, blog posts).
&

\textbf{Partner-Sourced Leads.}
\textbf{Downloads of Partner Plugins.}
\\
\addlinespace
\textbf{Initial Sales Team} &

\textbf{First Hires:} Hire another Account Executives to handle inbound leads and begin targeted outbound prospecting.
\textbf{Sales Playbook:} Formalize the sales process based on lessons from the founder-led sales phase.
&

\textbf{Qualified Demos per Month.}
\textbf{Average Sales Cycle Length (On-Premise).}
\\
\bottomrule
\end{tabularx}
}
\end{table}

\newpage
% --- YEAR 3 ---
\subsection{Year 3: Scaling \& Segment Leadership}
\textbf{Main Focus:} Accelerating growth, dominating the technical team niche, and establishing IntellyHub as a thought leader in the AI orchestration market.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tabularx}{\textwidth}{L L L}
\toprule
\textbf{Key Channels} & \textbf{Concrete Actions} & \textbf{Success KPIs} \\
\midrule
\textbf{Sales Scalability} &

\textbf{Team Expansion:} Grow the sales team to cover different geographies or industry verticals.
\textbf{Indirect Channels:} Begin exploring partnerships with System Integrators and Resellers.
&

\textbf{Annual Recurring Revenue (ARR) Growth.}
\textbf{Customer Acquisition Cost (CAC) and LTV/CAC Ratio.}
\\
\addlinespace
\textbf{Brand Marketing} &

\textbf{Thought Leadership:} Publish industry reports based on aggregated platform data.
\textbf{Sponsorships:} Sponsor key conferences and podcasts in the DevOps and AI space.
&

\textbf{Mentions in Industry Press.}
\textbf{Growth in Direct \& Branded Traffic.}
\\
\addlinespace
\textbf{Network Effect} &

\textbf{Open the Store:} Open the Automation Store and Plugin Marketplace to external contributions certificates partners.
\textbf{Developer Program:} Launch a formal Developer Relations (DevRel) program.
&

\textbf{Number of Community-Created Plugins/Templates.}
\textbf{Net Revenue Retention (NRR):} >110\%.
\\
\bottomrule
\end{tabularx}
}
\end{table}

\clearpage
\section{Operations Plan}
% Come funzionerà l'azienda giorno per giorno.
\subsection{Introduction}
This document outlines the operational plan to execute IntellyHub's development and go-to-market strategy. The plan is aligned with the phases of the Product Development Roadmap and describes the key activities for each functional area of the company.
