\midrule
\textbf{Team Execution \& Key-Person Risk} & The plan relies on hiring a small number of highly specialized individuals. The success of the project is highly dependent on this core team's ability to execute across product, infrastructure, and sales. The departure of a key member could cause significant delays. \\
\addlinespace
\textbf{Technological Complexity} & The tech stack (Kubernetes, multi-step AI pipelines, hybrid IDE) is extremely powerful but also complex to maintain and evolve. Bugs, security vulnerabilities, or performance bottlenecks in this complex system can be difficult and costly to resolve. \\
\addlinespace
\textbf{Hybrid Technology Risk (IDE/YAML Sync)} & Maintaining a perfect, real-time, bidirectional synchronization between the complex visual IDE and the textual YAML representation is technically demanding. It is a potential source of subtle and hard-to-debug bugs that could affect user trust. \\
\addlinespace
\textbf{Ecosystem Quality Control} & The value of the Automation Store and Plugin Marketplace is a double-edged sword. Low-quality, insecure, or poorly maintained community contributions could damage user trust and the platform's reputation. \\
\bottomrule
\end{tabularx}
\end{table}

\newpage
\subsection{Financial Risks}
\textit{Risks related to cash flow, funding, and financial sustainability.}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{@{}lL@{}}
\toprule
\textbf{Risk} & \textbf{Description} \\
\midrule
\textbf{High Initial Burn Rate} & The aggressive hiring plan results in a high monthly operational cost  before significant revenue is generated. This creates immense pressure to achieve product-market fit and generate revenue quickly. \\
\addlinespace
\textbf{Funding Dependency} & The business model is not designed for short-term profitability. Failure to meet the growth KPIs expected by investors is an existential threat. \\
\addlinespace
\textbf{Pricing Model Validation} & The proposed value metrics (executions, active automations) are logical but untested. An incorrect pricing model could lead to customer friction (if too expensive) or leave significant revenue on the table (if too cheap). \\
\bottomrule
\end{tabularx}
\end{table}

\newpage
\subsection{Mitigation Strategies}
\textit{Concrete actions to address and reduce the identified risks.}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{@{}lL@{}}
\toprule
\textbf{Risk Category} & \textbf{Mitigation Strategy} \\
\midrule
\textbf{Market Risks} & 
\textbf{Positioning \& Education:} Focus marketing not on replacing a single script, but on eliminating the long-term chaos of managing \textit{many} scripts. Use case studies like "Esplorado" to provide undeniable proof of value. \newline\newline
\textbf{Hybrid GTM:} Run the PLG (SaaS) and SLG (On-premise) motions in parallel. Use the faster feedback loop from the PLG side to refine the product and messaging for the slower enterprise sales cycle. \newline\newline
\textbf{Strategic AI Roadmap:} Position the current AI as the pragmatic, secure, and reliable choice for production environments. Frame the roadmap as an evolution towards more autonomous capabilities, building on the robust foundation we have today. \\
\addlinespace
\textbf{Operational Risks} & 
\textbf{Documentation \& Cross-Training:} Invest heavily in internal documentation from day one. Implement a culture of knowledge sharing and pair programming to reduce dependency on single individuals. \newline\newline
\textbf{Invest in Observability \& Testing:} Dedicate resources to a robust automated testing suite and integrate an APM (Application Performance Monitoring) tool early on to proactively identify and resolve issues. The test suite specifically covers the IDE/YAML sync logic. \newline\newline
\textbf{Curated Ecosystem:} Initially, the Store will only feature "Official" and "Verified Partner" plugins. Implement a clear and rigorous review process for all future community submissions, including automated security scans and quality checks. \\
\addlinespace
\textbf{Financial Risks} & 
\textbf{Milestone-Based Spending:} Tie major increases in spending (especially on marketing and sales hires) to the achievement of specific, pre-defined milestones (e.g., reaching the first 10 paying customers, achieving a certain retention rate). \newline\newline
\textbf{Continuous Investor Relations:} Maintain a transparent and regular communication channel with current and potential future investors, sharing progress on KPIs to build confidence and streamline the next funding round. \newline\newline
\textbf{Pricing Iteration:} Launch with a simple, flexible pricing model. Engage directly with early customers to understand the value they are getting and be prepared to iterate on the pricing structure based on their feedback and usage data. \\
\bottomrule
\end{tabularx}
\end{table}

% \newpage
% \subsection{Product Screenshots}
% Screenshot, mockup o diagrammi del prodotto.

\newpage
% Aggiungi qui eventuali fonti, studi o articoli citati nel documento.
\begin{thebibliography}{99}
    \bibitem{AIMarket}
    Market.us, \textit{Automated Machine Learning Market Report}, Available at: \url{https://market.us/report/automated-machine-learning-market/}, March~2025.
    
    \bibitem{MLOpsMarket}
    MarketReserchFuture.com, \textit{Mlops Market Research Report: Information By Component (Service, Platform), By Deployment Mode (On-Premises, Cloud), By Organization Size (Large Enterprise, SME's), By Verticals (BFSI, Retail and e-Commerce, Government and Defense, Healthcare and Life science, Manufacturing, and Others) And By Region (North America, Europe, Asia-Pacific, And Rest Of The World) –Market Forecast Till 2034.}, Available at: \url{https://www.marketresearchfuture.com/reports/mlops-market-18849}, Agoust~2025.
    
    \bibitem{AIOrch}
    Market.us, \textit{AI Orchestration Platform Market Report (2024--2034 Forecast)}, February~2025.  
    Available at: \url{https://market.us/report/ai-orchestration-platform-market/}.

    \bibitem{GartnerAgentic}
    Reuters (reporting Gartner), \textit{Over 40\% of agentic AI projects will be scrapped by 2027 … by 2028, 33\% of enterprise software will include agentic AI and 15\% of decisions will be made autonomously,} June~25,~2025.  
    Available at: \url{https://www.reuters.com/business/over-40-agentic-ai-projects-will-be-scrapped-by-2027-gartner-says-2025-06-25/}.

