    \end{itemize}
\end{itemize}

\subsubsection{Go-to-Market (Marketing \& Sales)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q5-Q6:}
    \begin{itemize}
        \item \textbf{Vertical Content Marketing:} Scale the production of content (case studies based on Design Partners, articles) focused on the chosen vertical.
        \item \textbf{Hiring:} Begin the recruitment process for the first Developer Advocate.
    \end{itemize}
    \item \textbf{Q7-Q8:}
    \begin{itemize}
        \item \textbf{Paid Plans Launch:} Finalize pricing (validated with Design Partners) and officially launch the Pro and Enterprise plans.
        \item \textbf{Sales Playbook (v1):} Begin documenting the sales process for enterprise customers.
    \end{itemize}
\end{itemize}

\clearpage

% --- PHASE 3 ---
\subsection{Phase 3: Leadership and Innovation (Quarters 5-6)}
\textbf{Strategic Objective:} To establish market leadership, create a network effect through the community, and **leverage data to build an insurmountable competitive advantage.**

\subsubsection{Product Development \& Engineering}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q9-Q10:}
    \begin{itemize}
        \item \textbf{Store Opening:} Open the Store to allow content submission from the community.
        \item \textbf{Moderation:} Implement internal tools for the review and validation of external contributions.
    \end{itemize}
    \item \textbf{Q11-Q12:}
    \begin{itemize}
        \item \textbf{(Revised) Data Platform \& Observability:} Develop the system for collecting and aggregating flow performance metrics, with the strategic goal of \textbf{building a "Data Moat"}.
        \item \textbf{Analytics Dashboard:} Create the user interface for visualizing analytics.
        \item \textbf{Proactive AI:} Improve "auto-healing" and proactive optimization features, \textbf{trained on aggregated platform data}.
    \end{itemize}
\end{itemize}

\subsubsection{Go-to-Market (Marketing \& Sales)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q9-Q10:}
    \begin{itemize}
        \item \textbf{Sales Team Scaling:} Hire additional Account Executives to cover specific markets or verticals.
        \item \textbf{Thought Leadership:} Begin publishing reports and analyses based on platform usage data.
    \end{itemize}
    \item \textbf{Q11-Q12:}
    \begin{itemize}
        \item \textbf{Brand Marketing:} Increase investment in brand awareness activities (sponsorships, events).
    \end{itemize}
\end{itemize}

\newpage
\section{Risk Analysis}
\subsection{Market Risks}
\textit{Risks related to the market, competition, and customer adoption.}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{@{}lL@{}}
\toprule
\textbf{Risk} & \textbf{Description} \\
\midrule
\textbf{Competition from the "Status Quo"} & Our biggest competitor is not another platform, but the inertia of developers using custom Python scripts. Their familiarity and the perceived zero initial cost make it a significant hurdle to overcome. \\
\addlinespace
\textbf{Slow Enterprise Adoption Cycle} & The on-premise and enterprise sales model is crucial for high-value contracts, but it is characterized by long sales cycles (6-12+ months) and complex proof-of-concept (POC) phases. A delay in closing the first key enterprise deals could significantly impact revenue projections. \\
\addlinespace
\textbf{AI Technology Shift} & Our AI is currently positioned as a "copilot." A rapid technological leap by a competitor towards a truly autonomous AI agent that is "good enough" could make our more controlled, structured approach seem less innovative. \\
\bottomrule
\end{tabularx}
\end{table}

\newpage
\subsection{Operational Risks}
\textit{Risks related to technology, personnel, and execution.}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{@{}lL@{}}
\toprule
\textbf{Risk} & \textbf{Description} \\
