
\section{Go-to-Market Strategy}
% Come raggiungerai i tuoi clienti?

IntellyHub's Go-to-Market (GTM) strategy is based on a hybrid model that combines two growth engines:
\begin{enumerate}
    \item \textbf{Product-Led Growth (PLG) for SaaS:} We leverage the superiority of the product, a Free Tier, and the Automation Store to attract, activate, and convert users in a scalable, bottom-up fashion.
    \item \textbf{Sales-Led Growth (SLG) for On-Premise \& Enterprise:} We use a targeted, consultative sales approach to win large customers with complex security and governance needs.
\end{enumerate}
These two engines are designed to be mutually reinforcing: the success of the PLG motion generates leads and brand awareness for the sales team.

% --- Strategic Objectives ---
\subsection{Strategic Objectives (3-Year Horizon)}
\begin{itemize}
    \item \textbf{Positioning:} To become a leading platform for orchestrating complex automations and AI workflows for modern technical teams.
    \item \textbf{Adoption:} To achieve critical mass of active users and a vibrant community around the plugin ecosystem and the automation store.
    \item \textbf{Revenue:} To build a sustainable business model with significant Annual Recurring Revenue (ARR), driven by both SaaS subscriptions and enterprise on-premise contracts.
\end{itemize}

% --- YEAR 1 ---
\subsection{Year 1: Foundation \& Market Validation}
\textbf{Main Focus:} Winning over early adopters, validating product-market fit, and securing the first key reference customers (both SaaS and On-Premise). In this phase, many activities are manual and "do not scale."

\newpage
\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tabularx}{\textwidth}{L L L} 
\toprule
\textbf{Key Channels} & \textbf{Concrete Actions} & \textbf{Success KPIs} \\

\midrule
\textbf{Product-Led Growth (PLG)} & 
\textbf{Niche Launch:} Present IntellyHub on platforms like Product Hunt, Hacker News, and relevant technical subreddits (e.g., r/devops, r/kubernetes).\newline\newline
\textbf{Automation Store:} Populate the store with 20-30 high-quality official templates that solve real, painful problems.
&
\textbf{Activation Rate:} >25\% (users running their first automation within 7 days).\newline\newline
\textbf{1-Month Retention:} >15\% (users returning after 4 weeks).
\\
\addlinespace

\textbf{Technical Content Marketing} & 
\textbf{Blog \& Tutorials:} Publish 2-4 in-depth technical articles per month showcasing how to solve specific problems with IntellyHub.\newline\newline
\textbf{Video Content:} Create concise video tutorials.
&
\textbf{Qualified Traffic:} Number of site visits from organic and referral channels.\newline\newline
\textbf{Visitor-to-Signup Rate:} >2\%.
\\
\addlinespace

\textbf{Community Building} &
\textbf{Discord/Slack Channel:} Establish a central hub for early users.\newline\newline
\textbf{Founder-led Support:} Personally answer every question and feedback request to build a strong rapport.
&
\textbf{Community Engagement:} Weekly active members, peer-to-peer support interactions.\newline\newline
\textbf{Qualitative Feedback:} Minimum of 5 in-depth user interviews per month.
\\
\addlinespace

\textbf{Founder-Led Sales (On-Premise)} &
\textbf{Leverage Network:} Founders personally manage the first 3-5 sales processes with target companies from their own network.\newline\newline
\textbf{Proof of Concept (POC):} Focus on the success of a few high-value POCs.
&
\textbf{POCs Initiated:} 3-5 throughout the year.\newline\newline
\textbf{On-Premise Contracts Signed:} 1-2 key reference customers.
\\
\bottomrule
\end{tabularx}
}
\end{table}


% --- YEAR 2 ---
\subsection{Year 2: Expansion \& Building a Repeatable Growth Engine}
\textbf{Main Focus:} Transforming initial value into scalable, repeatable processes. Optimizing what worked in Year 1 and building the foundation of a commercial team.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tabularx}{\textwidth}{L L L}
