        \item \textbf{Versioning:} Add history and rollback functionality for automations.
    \end{itemize}
    \item \textbf{Q4:}
    \begin{itemize}
        \item \textbf{On-Premise:} Develop and test the on-premise version of the platform for enterprise customers.
        \item \textbf{RBAC:} Implement a Role-Based Access Control system for team management.
    \end{itemize}
\end{itemize}

\subsubsection*{Go-to-Market (Marketing \& Sales)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q3:}
    \begin{itemize}
        \item \textbf{Vertical Content Marketing:} Scale the production of content (case studies based on Design Partners, articles) focused on the chosen vertical.
        \item \textbf{Hiring:} Begin the recruitment process for the first Developer Advocate.
    \end{itemize}
    \item \textbf{Q4:}
    \begin{itemize}
        \item \textbf{Paid Plans Launch:} Finalize pricing (validated with Design Partners) and officially launch the Pro and Enterprise plans.
        \item \textbf{Sales Playbook (v1):} Begin documenting the sales process for enterprise customers.
    \end{itemize}
\end{itemize}

\clearpage

% --- PHASE 3 ---
\subsection{Phase 3: Leadership and Innovation (Quarters 5-6)}
\textbf{Strategic Objective:} To establish market leadership, create a network effect through the community, and **leverage data to build an insurmountable competitive advantage.**

\subsubsection*{Product Development \& Engineering}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q5:}
    \begin{itemize}
        \item \textbf{Store Opening:} Open the Store to allow content submission from the community.
        \item \textbf{Moderation:} Implement internal tools for the review and validation of external contributions.
    \end{itemize}
    \item \textbf{Q6:}
    \begin{itemize}
        \item \textbf{(Revised) Data Platform \& Observability:} Develop the system for collecting and aggregating flow performance metrics, with the strategic goal of \textbf{building a "Data Moat"}.
        \item \textbf{Analytics Dashboard:} Create the user interface for visualizing analytics.
        \item \textbf{Proactive AI:} Develop "auto-healing" and proactive optimization features, \textbf{trained on aggregated platform data}.
    \end{itemize}
\end{itemize}

\subsubsection*{Go-to-Market (Marketing \& Sales)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Q5:}
    \begin{itemize}
        \item \textbf{Sales Team Scaling:} Hire additional Account Executives to cover specific markets or verticals.
        \item \textbf{Thought Leadership:} Begin publishing reports and analyses based on platform usage data.
    \end{itemize}
    \item \textbf{Q6:}
    \begin{itemize}
        \item \textbf{Brand Marketing:} Increase investment in brand awareness activities (sponsorships, events).
    \end{itemize}
\end{itemize}

\section{Product Development Roadmap} % This section provides a detailed roadmap for the development of IntellyHub, outlining the strategic objectives and key activities for each phase of the product lifecycle. The roadmap is designed to ensure that the product evolves in a structured manner, addressing both immediate needs and long-term goals.
\subsection*{Introduction}
This roadmap outlines the planned development phases for IntellyHub, starting from its current state as an advanced prototype. The goal is to evolve the product into a robust, scalable, and market-leading platform. The roadmap is divided into four-month periods (Quarters) to provide a clear strategic vision.

\clearpage

% --- PHASE 1 ---
\subsection{Phase 1: From Prototype to Robust MVP (Quarters 1-2)}
\textbf{Strategic Objective:} To transform the prototype into a stable, secure Minimum Viable Product (MVP) ready for its first early adopters.

\subsubsection*{Quarter 1 (Months 1-4): Stabilization and Foundations}
\begin{itemize}[leftmargin=*]
    \item \textbf{Core Platform \& Backend:}
    \begin{itemize}
        \item Finalize and document the plugin API.
        \item Implement a basic logging and monitoring system for flow executions.
        \item Complete the unit and integration test suite for the core engine.
    \end{itemize}
    \item \textbf{Frontend \& IDE:}
    \begin{itemize}
        \item Refine the UI/UX of the hybrid IDE to ensure flawless synchronization.
        \item Develop an in-app notification system for errors and successes.
        \item Improve error handling in the interface.
